Enhancement of SDR in Thessaloniki

### 2024-04-14 GHI_enh_06_sza.tex
Commit 2024-04-14 16:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-14}

@@

\begin{verbatim}
Not changed:  ./GHI_enh_06_sza.R 
Not changed:  ./GHI_enh_00_variables.R 
Not changed:  ./GHI_enh_03_process.R 
Not changed:  ./data/GHI_enh_03_process.Rda 
\end{verbatim}

\begin{verbatim}
[1] FALSE
\end{verbatim}

\begin{verbatim}
Written `R_make_` file: .//.R_make.mk 
\end{verbatim}

@@

\begin{verbatim}
2024-03-14 09:41:49.6 athan@tyler GHI_enh_06_sza.R 0.259163 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-14}

@@

@@

\begin{verbatim}
2024-04-14 00:55:04.2 athan@tyler GHI_enh_06_sza.R 0.288979 mins
\end{verbatim}
